Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-01 robdml.tex
tex

\cref{tab:ics}

\subsection{Comparison with State-of-the-art}
\label{sec:43}

@@

>>>>

@@

\subsection{Comparison to State-of-The-Art Defense}
\label{sec:43}

After validating the effectiveness of our proposed method, we conduct
experiments on three commonly used DML datasets to compare our proposed method
with the state-of-the-art defense methods, as shown in \cref{tab:sota}.
